\documentclass[14]{article}

% Used packages
\usepackage{apacite}
\usepackage[12pt]{moresize}
%\usepackage[numbers,sort&compress]{natbib}
\usepackage{blindtext}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[explicit,noindentafter]{titlesec}
\usepackage[rightcaption]{sidecap}
\usepackage{caption}
\usepackage{float}
\usepackage{csquotes}
\usepackage{titling}
\usepackage{titlesec}
\usepackage{graphicx} %package to manage images
\graphicspath{{images/}}



\titlespacing\section{1pt}{12pt plus 0pt minus 0pt}{6pt plus 0pt minus 0pt}
\titlespacing\subsection{1pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}
\titlespacing\subsubsection{1pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}
\titlespacing\paragraph{1pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}

% New commands
\newcommand{\addsection}[3]{\addtocontents{toc}{\protect\contentsline{section}{\protect\numberline{#1}#2}{#3}}}
\newcommand{\addsubsection}[3]{\addtocontents{toc}{\protect\contentsline{subsection}{\protect\numberline{#1}#2}{#3}}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\tab}[1]{\hspace{.5\textwidth}\rlap{#1}}
\newcommand{\Csh}{C{\lserif\#}}


\begin{document}
\author{\textbf{Faculty of Sciences and Bio-Engineering Sciences}\\[2\baselineskip]\newline\textbf{Arthur Chomé - 0529279}}

\date{ \LARGE Assignment 3: Review}
\title{\vspace{-6cm}}%\underline{Everything is connected}}

\maketitle

\section{Introduction}
Based on our student number (0529279), we had the option between paper 2, 4 and 9 to write our review about. We went for paper number 4\cite{dandekar2013biased} discussing the issue of opinion polarisation within society and a mathematical model as to measure to which degree opinions of a given set diverge. Thus implying polarisation. 
\newline 
It starts by explaining the factors that lead to this phenomenon which include homophily --interaction between like-minded individuals-- and biased assimilation whereupon individuals --when confronted with inconclusive evidence on a complex issue-- draw undue support to their own position on the matter, are the leas. After a --quite misleading-- introduction on the issue of polarisation and their contributing factors, it refers to DeGroot's model\cite{degroot1974reaching} for opinion formation criticizing it for its lack of inclusion of biased assimilation. Its contributions are an improved model with biased assimilation applied on a network model of individual opinions --linked to each other if the persons know each other-- taking the form of a directed graph. It also analyses 3 recommender algorithms that present data over the internet to a user based on his own convictions and how this may possibly lead to polarisation.The paper gave us a good review of the mathematical possibilities to measure polarisation within a network of opinions linked to a larger group. It's a surprise to read that even the most complex social problems can be mathematically expressed as models and explained using graph theory.

\section{Opinion}
The paper's subject is good --trying to mathematically measure the social problem of polarisation-- but it lacks the necessary touch to make it attractive for political or social scientists who would profit the most from this article. Its introduction is bad discussing polarization and all additional concepts but the content following upon it goes into advanced mathematical domains without teasing it beforehand making it very misleading and confusing.
\newline
If we were only to base ourselves on the introduction of the paper --its writing style and title-- we might convince ourselves that it was written for a target audience with no explicit mathematical background such as political scientists or psychologists. However, the paper shifts directly towards a mathematical focus introducing rather complex notions about graph theory and models making for a bad writing style.
Another fault of the paper is has a bad overall structure. Though it provides an introduction, the separation between related work, experiments and conclusion is not sufficient. 
\newline
The model uses three recommender algorithms as to measure to which extent they cause polarisation on the internet when biased assimilation is present: SALSA\cite{lempel2001salsa}, Personalized PageRank\cite{page1999pagerank}, and item-based collaborative filtering\cite{linden2003amazon} respectively. Though they are properly referred, they only provide mathematical formulas to explain the workings of each algorithm making it very hard to follow. Another problem is that the link between DeGroot's model and the analysis with these recommender algorithms lacks clarity. A summary on the tests being performed that indicate increased or decreased polarization is missing making it harder to believe these claims. It mentions a graph of opinions to apply the model on but does not elaborate on this. It does not show any example data which makes it hard for the user to follow. 

\section{Improvements}
For the above critique on the paper, we have some suggestions for improvements to be made. This would in turn increase the relative attractiveness of the paper increasing its influence. The following suggestions are focusing on the writing the style, the paper's structure and the discussion of algorithms.

\subsection{Content, Writing Style \& Structure}
The paper's introduction focuses too much on the terminology and concepts of polarization. It is misleading to be afterwards discussing the paper's extension of DeGroot's mathematical consensus model for the explanation of divergence in opinions. A suggestion is to shorten the paper's introduction on polarization and focus more on the mathematical model they developed for it. The title of the paper should be reworked, it does not stick with the actual content of the paper. 
%\newline
After the introduction, the paper is full of definitions and formulas on mathematical models making it very difficult to follow. I suggest to remove the definitions in the paper in exchange for a more high-level, easy-to-understand explanation all the while referring to papers citing these definitions. The use of figures should not be excluded.
\newline
Finally, the overall structure of the paper should be reworked with a clear related work section about DeGroot's model, a discussion about the used node graphs and the Network Disagreement Index. After this comes a discussion of the extension of the model and the experiment with recommender algorithm followed by a clear conclusion.

\subsection{Overview of Analysis}
Providing an Appendix on the results of the polarizing nature of recommender algorithms is a good start but it should be integrated within the paper as to be more clear for the readers. It should give a hands-on comparison of the scores for each algorithm and clarify which difference it would yield if we were to use DeGroot's algorithm without biased assimilation.
\newline
As to verify the result of the model, the experiment could be recreated in real-life with a sample population. Recommender algorithms work to provide customized news feeds to each user and the internet does not lack API's to recreate these situations in a measured environment.

\subsection{Algorithm Performance Comparison}
The inclusion of pseudocode\footnote{\protect\url{https://en.wikipedia.org/wiki/Pseudocode}} for each algorithm should not be missed. It provides a high-level description of each of their operation. Although all three algorithms operate by ways of random walks on a node graph G, there is a performance comparison to be made. One of the biggest concerns in Computer Science is to perform work as efficient as possible without wasting resources. This is why a table of the best, worst and average case performance of each algorithm should be provided in Big-O notation\footnote{\protect\url{https://en.wikipedia.org/wiki/Big\_O\_notation}}

%From the perspective of a Computer Science student, the algorithms referenced in this paper are not clearly explained in terms of workings or application. Adding pseudocode or other code snippets could alleviate this instead of using the pure mathematical formulas. Another problem

%proposes a mathematical model based on DeGroot's model\cite{degroot1974reaching} that also accounts for biased assimilation. proposed a process where at each time step, individuals simultaneously update their opinion to the weighted average of their neighbors’ and their own opinionat the previous time step.


%the paper offers a mathematical model as to measure the extend to which opinions within a group can diverge. It is represented as a graph of nodes representing persons and their opinions on a subject (e.g. religion, freedom of speech,...) with the graph's edges the relationships between them. For each relationship, there is an added weight representing the degree to which two nodes influence each other's opinion. As to measure the degree in which the opinions differ, the paper formulated a Network Disagreement Index.
%\newline 
%DeGroot\cite{degroot1974reaching} proposed a process where at each time step, individuals simultaneously update their opinion to the weighted average of their neighbors’ and their own opinion at the previous time step.

%The degree to which opinions diverge in this matter is made clear 

%It offers a formation process for biased opinion formation process.
%Polarisation has increased in American society brought about by recent technology trends such as the internet, talk shows and cable news. Reason for this is that individuals are being confronted with a high rate of diverging opinions enabling them to select information conforming to their own standings leading to more extreme beliefs.

%Contributing factors to this are homophily within groups and biased assimilation. Homophily refers to the  

%Polarization in this sense of the word refers to an increased divergence of opinions within individuals of a group. opinion formation process is polarizing if it results in increased divergence of opinions.



%\subsection{Graph Theory}

%\paragraph{Strengths}

%\paragraph{Weaknesses}

%\section{Improvements}

%\section{Conclusion}

\bibliographystyle{apacite}
\bibliography{bibliography}	
\end{document}
